---
title: "Exploring Potentials of Computational Text Analyis in the Study of Radicalism"
subtitle: "Supplement: Code and Output for Reproducibility"
author:
  - name: Nader Hotait
    affiliations:
      - name: Humboldt-Universität zu Berlin
        url: mailto:nader.hotait@hu-berlin.de
      - name: Universität Mannheim
        url: mailto:nhotait@mail.uni-mannheim.de
    orcid: 0000-0003-4211-5300
    attributes:
      corresponding: true
format:
  html:
    code-fold: true
    toc: true
    toc-location: left
execute:
  cache: false
  eval: true
---

## Preamble

```{r}
#| warning: false

# Packages
pacman::p_load(tidyverse, readxl, ggrepel, lubridate, ggpubr, quanteda,
               quanteda.textplots, quanteda.textstats, quanteda.textmodels,
               grid, gridExtra, Cairo, ldatuning, stm, tidytext, seededlda,
               caret, glmnet, tibble, kableExtra, caretEnsemble, methods)

# Figure Path
dir.create(file.path(getwd(), "figs"), showWarnings = FALSE)

# Data
## Scopus
scopus <- bind_rows(
  read_excel("Scopus-125886-Analyze-Year.xlsx"),
  read_excel("Scopus-43368-Analyze-Year.xlsx"),
  read_excel("Scopus-85-Analyze-Year.xlsx"),
  read_excel("Scopus-20678-Analyze-Year.xlsx")
)

scopus$query <- factor(scopus$query, levels = c("CTA", "CTA in SOCI", "Radicalism", "CTA+Radicalism"))

## Generation Islam
genislam <- readRDS("genislam.RDS")

## ZMD
zmd <- readRDS("zmd")

## All Islam Actors
all_islam <- bind_rows(genislam,
                       zmd,
                       readRDS("alhm"),
                       readRDS("ditib"),
                       readRDS("igmggenclik"),
                       readRDS("islamratbrd"))
```

## Introduction: Scopus Query

```{r}
#| label: scopus-analysis-1
#| fig-cap: Publications listed on Scopus between 2001-2021.
#| warning: false

scopus_table <- scopus %>%
  filter(year==2001 | year==2021) %>%
  pivot_wider(names_from = year, values_from = n)

names(scopus_table) <- c("Query", "2021", "2001")
scopus_table <- scopus_table[c(1,4,2,3), c(1,3,2)]
scopus_table[4,2] <- 0

graph_table <- ggtexttable(scopus_table, rows = NULL, theme = ttheme("light"))

# Creating Figure
scopus_grph <- scopus %>%
  filter(year>=2001) %>%
  ggplot(aes(x=year, y=n, fill=query)) +
  geom_point(aes(shape=query), size = 1.5) +
  geom_line(aes(linetype=query)) +
  theme_minimal() +
  xlab("Year") +
  ylab("Number of Publications") +
  theme(legend.position="bottom") +
  guides(fill=guide_legend(title="Search Query:"),
         shape=guide_legend(title="Search Query:"),
         linetype=guide_legend(title="Search Query:"))

scopus_grph + annotation_custom(ggplotGrob(graph_table),
                              xmin = 2002.5, ymin = 8100,
                              xmax = 2007.5)
# Saving Figure
ggsave("scopus_1.pdf", path = file.path(getwd(), "figs"), device="pdf", dpi=800)
```

**Query Method:** For the query of the subject fields, terms were searched for within the titles, abstracts, and keywords of publications listed on Scopus. For the query related to Computational Text Analysis in social sciences (CTA in SOCI) and Radicalism, the search was limited to the Scopus subject category "social sciences". This is also due to the fact that terms related to the root word "radical" often have a different meaning in the natural sciences. For the search query related to CTA, related domains (e.g. Quantitative Text Analysis and Natural Language Processing), as well as common methods also searched for.

Search Terms:

-   Computational Text Analysis (CTA): ((TITLE-ABS-KEY ("quantitative text" OR "computational text" OR "natural language processing" OR "quantitative content analysis" OR "quantitative content analyses") OR TITLE-ABS-KEY("sentiment analysis" OR "sentiment analyses" OR "named entity recognition" OR "topic model" OR "topic modeling" OR "topic models") OR TITLE-ABS-KEY("text classification" OR "key word extraction" OR "lemmatization" OR "word embedding")))

-   Computational Text Analysis in Social Sciences (CTA IN SOCI): CTA AND ( LIMIT-TO ( SUBJAREA,"SOCI" ) ) )

-   Radicalism: ((TITLE-ABS-KEY (radicali OR terrorist OR terrorism OR "political violence" OR extremi OR "far left" OR "far right" OR islamist OR islamism OR fundamentalis OR jihad) ) AND ( LIMIT-TO ( SUBJAREA,"SOCI" ) ) )

-   CTA+Radicalism: Intersection of the CTA and Radicalism query

## Tweet Frequency of Genislam1

```{r}
#| label: gen-islam-1
#| fig-cap: "Account Activity of Generation Islam (@genislam1) between August 2019 and April 2022: (a) Cumulative tweets over time. (b) Weekly tweet frequency with generalized additive mode smoothing."
#| warning: false

# Creating Figure
Sys.setlocale("LC_TIME", "English")
ts <- genislam
ts$tweet <- 1L

ts <- ts %>%
  mutate(weekly = str_c(
    formatC(isoweek(created_at), format = "f", digits = 0, width = 2, flag = "0"), 
    "/", 
    str_sub(isoyear(created_at), 3, 4))) %>%
  group_by(screen_name) %>%
  arrange(created_at, .by_group = TRUE) %>%
  mutate("cum" = cumsum(tweet))

ts <- ts %>%
  group_by(screen_name, weekly) %>%
  mutate("week_cum" = cumsum(tweet))

cum_tweet <- ggplot(ts) +
  geom_line(aes(x=as.Date(created_at), y=cum)) +
  xlab("Date") +
  ylab("Tweets (cumulative)") +
  scale_x_date(date_labels = "%b %y", date_breaks = "2 month") +
  theme_minimal() +
  labs(title = "A") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


week_tweet <- ggplot(ts) +
  geom_point(aes(x=as.Date(created_at), y=week_cum), alpha = 0.1) +
  geom_smooth(aes(x=as.Date(created_at), y=week_cum), se = FALSE, color = "black", 
              method = "gam", formula = y ~ s(x)) +
  xlab("Date") +
  ylab("Tweets (weekly)") +
  scale_x_date(date_labels = "%b %y", date_breaks = "2 month") +
  theme_minimal() +
  labs(title = "B") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggarrange(cum_tweet, week_tweet, ncol = 1, nrow = 2, align = "v")

# Saving Figure
ggsave("tweets_genislam.pdf", path = file.path(getwd(), "figs"), device="pdf", dpi=800)
```

## Preprocessing

```{r}
#| label: preprocessing
#| fig-cap: "Text elements: (a) Before and (b) after preprocessing"
#| warning: false

# Creating Figure
## Without preprocessing
dfm_pre <- corpus(genislam) %>%
  dfm() %>%
  dfm_group(groups = screen_name)

## With preprocessing
post_genislam <- genislam
post_genislam$text <- gsub("🇵🇸", "",
                gsub("🏽","",
                     gsub("🏼","",
                          gsub("✊","", 
                               gsub("🏻", "", 
                                    gsub("🤦","", 
                                         gsub("♂️","",
                                              gsub("👨","",
                                                   gsub("👏", "", 
                                                        gsub("🤲🏾", "", 
                                                              gsub("🤲", "", 
                                                                    gsub("💔", "", 
                                                                         gsub(" 👇", "", post_genislam$text)))))))))))))
post_genislam$text <- gsub("🤷","", 
                           gsub("🤷‍","", 
                                gsub("♀", "",
                                     gsub("🤷‍♀", "", 
                                          gsub("🇨🇳","", post_genislam$text)))))

dfm_post <- corpus(post_genislam) %>%
  tokens(remove_punct=T,
         remove_numbers = T,
         remove_url = T, 
         split_hyphens = T,
         remove_symbols = T) %>%
  tokens_remove(stopwords("english", source = "marimo")) %>%
  tokens_remove(stopwords("de", source = "marimo")) %>%
  tokens_remove(stopwords("ar", source = "stopwords-iso")) %>%
  tokens_remove(c("à", "un", "la", "le", "en", "et", "été", "les", "avec")) %>%
  tokens_remove(pattern = "^[\\p{script=Arab}]+$", valuetype = "regex") %>%
  dfm() %>%
  dfm_remove(pattern = c("*.tt", "*.uk", "*.com", "rt", "#*", "@*", ".de")) %>%
  dfm_trim(max_termfreq = .99,termfreq_type = "quantile",verbose = T) %>%
  dfm_trim(min_termfreq = .7,termfreq_type = "quantile",verbose = T) %>%
  dfm_wordstem()

saveRDS(dfm_post, "dfm_post.RDS") ## Save for cache issues

pre_pp <- textstat_frequency(dfm_pre, n = 50)

pre_pp$feature <- with(pre_pp, reorder(feature, -frequency))

pp_1 <- ggplot(pre_pp, aes(x = feature, y = frequency)) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Frequency") +
  xlab("Text elements (without preprocessing)") +
  labs(title = "A")

post_pp <- textstat_frequency(dfm_post, n = 50)

post_pp$feature <- with(post_pp, reorder(feature, -frequency))

pp_2 <- ggplot(post_pp, aes(x = feature, y = frequency)) +
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylab("Frequency") +
  xlab("Text elements (with preprocessing)") +
  labs(title = "B")

ggarrange(pp_1, pp_2, ncol = 1, nrow = 2, align = "v")

# Saving Figure
ggsave("preprocessing.pdf", path = file.path(getwd(), "figs"), device="pdf", dpi=800)
```

## Exploring Content: Wordclouds

```{r}
#| label: word-clouds-1
#| warning: false
#| fig-cap: "Word cloud"
## Create function
create_wordclouds <- function(data, ngram=1, seed=123, color = "gray20", 
                              max_words=100, name = "1"){
  df <- data
  df$text <- gsub("&amp;", "and", df$text, ignore.case = TRUE)
  df$text <- gsub("&", "and", df$text, ignore.case = TRUE)
  df$text <- gsub("Ben and Jerry", "Ben_and_Jerry", df$text, ignore.case = TRUE)
  df$text <- gsub("🇵🇸", "",
                gsub("🏽","",
                     gsub("🏼","",
                          gsub("✊","", 
                               gsub("🏻", "", 
                                    gsub("🤦","", 
                                         gsub("♂️","",
                                              gsub("👨","",
                                                   gsub("👏", "", 
                                                        gsub("🤲🏾", "", 
                                                              gsub("🤲", "", 
                                                                    gsub("💔", "", 
                                                                         gsub(" 👇", "", df$text)))))))))))))
  wordcloud <- corpus(df) %>%
  tokens(remove_punct=T,
         remove_numbers = T,
         remove_url = T, 
         split_hyphens = T,
         remove_symbols = T) %>%
  tokens_remove(stopwords("english")) %>%
  tokens_remove(stopwords("de", source = "marimo")) %>%
  tokens_ngrams(n=ngram) %>%
  dfm() %>%
  dfm_remove(pattern = c("*.tt", "*.uk", "*.com", "rt", "#*", "@*", ".de"))
set.seed(seed)
cairo_pdf(paste0(file.path(getwd(), "figs"), "/","wc-", name, ".pdf"), fallback_resolution=800)
wordcloud %>%
  textplot_wordcloud(max_words = max_words, color = color)
dev.off()
set.seed(seed)
wordcloud %>%
  textplot_wordcloud(max_words = max_words, color = color)
}

# Creating and Saving Figure 
create_wordclouds(genislam, seed = 100)
```

```{r}
#| label: word-clouds-2
#| warning: false
#| fig-cap: "Word cloud (Bigram)"
create_wordclouds(genislam, seed = 100, ngram = 2, name = "2")
```

```{r}
#| label: word-clouds-3
#| warning: false
#| fig-cap: "Word cloud (Trigram)"
create_wordclouds(genislam, seed = 100, ngram = 3, name = "3")
```

## Exploring Content: Feature-occurrence matrix

```{r}
#| label: top-hashtags
#| warning: false
#| tbl-cap: 50 most used hashtags by @genislam1

# Create Data
tweet_dfm <- tokens(genislam$text, remove_punct = TRUE) %>%
  dfm() %>%
  dfm_select(pattern = "#*")

# Display 50 Most used Hashtags
toptag <- names(topfeatures(tweet_dfm, 50))
toptag_table <- bind_cols("1-10" = toptag[1:10],
                          "11-20" = toptag[11:20],
                          "21-30" = toptag[21:30],
                          "31-40" = toptag[31:40],
                          "41-50" = toptag[41:50])
knitr::kable(toptag_table)
```

```{r}
#| label: hashtag-occur
#| warning: false
#| fig-cap: Feature co-occurrence of 50 most used hashtags by @genislam1

# Creating Figure
tag_fcm <- fcm(tweet_dfm)

topgat_fcm <- fcm_select(tag_fcm, pattern = toptag)
set.seed(123)
textplot_network(topgat_fcm, min_freq = 0.1, edge_alpha = 0.8, edge_size = 5,
                 edge_color="grey60")

# Saving Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "feature_co_occur.pdf"), 
          fallback_resolution=800, height = 7, width = 10)
set.seed(123)
textplot_network(topgat_fcm, min_freq = 0.1, edge_alpha = 0.8, edge_size = 5,
                 edge_color="grey60")
dev.off()
```

## Exploring Content: Usernames

```{r}
#| label: user-occur
#| warning: false
#| fig-cap: User co-occurrence

# Creating Figure
user_dfm <- tweet_dfm <- tokens(genislam$text, remove_punct = TRUE) %>%
  dfm() %>%
  dfm_select(pattern = "@*")

topuser <- names(topfeatures(user_dfm, 80))
user_fcm <- fcm(user_dfm)
user_fcm <- fcm_select(user_fcm, pattern = topuser)
set.seed(123)
textplot_network(user_fcm, min_freq = 0.1, edge_color = "grey60", 
                 edge_alpha = 0.5, edge_size = 5)

# Saving Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "user_co_occur.pdf"), 
          fallback_resolution=800, height = 7, width = 10)
set.seed(123)
textplot_network(user_fcm, min_freq = 0.1, edge_color = "grey60", 
                 edge_alpha = 0.5, edge_size = 5)
dev.off()
```

## Exploring Content: Topic Modeling

```{r}
#| label: find-topics
#| warning: false
#| fig-cap: Metrics to determine optimal number of topics

# Creating Figure
dfm_post.new <- dfm_subset(dfm_post, ntoken(dfm_post) > 0)

result <- FindTopicsNumber(
  dfm_post.new,
  topics = seq(from = 2, to = 50, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed =1234),
  mc.cores = NA,
  verbose = FALSE)

# Create function to plot figure
lda_plot <- function (values)
{
  if ("LDA_model" %in% names(values)) {
    values <- values[!names(values) %in% c("LDA_model")]
  }
  columns <- base::subset(values, select = 2:ncol(values))
  values <- base::data.frame(values["topics"], base::apply(columns,
                                                           2, function(column) {
                                                             scales::rescale(column, to = c(0, 1), from = range(column))
                                                           }))
  values <- reshape2::melt(values, id.vars = "topics",
                           na.rm = TRUE)
  values$group <- values$variable %in% c("Griffiths2004",
                                         "Deveaud2014")
  values$group <- base::factor(values$group, levels = c(FALSE,
                                                        TRUE), labels = c("minimize", "maximize"))
  p <- ggplot(values, aes_string(x = "topics", y = "value",
                                 group = "variable"))
  p <- p + geom_line()
  p <- p + geom_point(aes_string(shape = "variable"),
                      size = 3)
  p <- p + guides(size = FALSE, shape = guide_legend(title = "Metrics:"))
  p <- p + scale_x_continuous(breaks = values$topics)
  p <- p + labs(x = "Number of topics", y = NULL)
  p <- p + facet_grid(group ~ .)
  p <- p + theme_bw() %+replace% theme(panel.grid.major.y = element_blank(),
                                       panel.grid.minor.y = element_blank(), panel.grid.major.x = element_line(colour = "grey60"),
                                       panel.grid.minor.x = element_blank(), legend.key = element_blank(),
                                       strip.text.y = element_text(angle = 90))
  p <- p + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  g <- ggplotGrob(p)
  g$layout[g$layout$name == "strip-right", c("l",
                                             "r")] <- 3
  grid::grid.newpage()
  grid::grid.draw(g)
}

# Plot
lda_plot(result)

# Saving Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "find_topics.pdf"),
          fallback_resolution=800, height = 7, width = 10)
lda_plot(result)
dev.off()
```

```{r}
#| label: searchK
#| warning: false
#| fig-cap: "``Stm'': Metrics to determine an optimal number of topics"

# Reload dfm_post because of cache issues
rm(dfm_post)
dfm_post <- readRDS("dfm_post.RDS")
dfm2stm <- convert(dfm_post, to = "stm")

set.seed(1234)
searchk <- searchK(dfm2stm$documents, dfm2stm$vocab, K = seq(6,18,2))
```

```{r}
#| label: searchK-plot
#| warning: false
#| fig-cap: "'Stm': Metrics to determine an optimal number of topics"
# Create Figure
plot(searchk)

#Saving Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "searchk.pdf"), 
          fallback_resolution=800, height =5, width = 7)
plot(searchk, main = "")
dev.off()
```

```{r}
#| label: Most relevant words per topic
#| warning: false
# STM model
topic.count <- 10
set.seed(1234)
model.stm <- stm(dfm2stm$documents, dfm2stm$vocab, 
                 K = topic.count, data = dfm2stm$meta, 
                 init.type = "Spectral", verbose = FALSE)

labelTopics(model.stm, n=20)
```

```{r}
#| label: stm-model
#| warning: false
#| fig-cap: Structural Topic Modeling with 10 topics
# Create Figure

par(bty="n",col="grey40",lwd=5)
plot(model.stm, type = "summary", text.cex = 1, main = "")

# Save Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "topic-model.pdf"), 
          fallback_resolution=800, height =5, width = 7)
par(bty="n",col="grey40",lwd=5)
plot(model.stm, type = "summary", text.cex = 1, main = "")
dev.off()
```

```{r}
#| label: stm-perspectives
#| warning: false
#| tbl-cap: "Topics, expected topic proportion, and highest probability words"

# Create Table Data
proportions_table <- make.dt(model.stm)  
topic_table <- summarize_all(proportions_table, mean)
topic_long <- topic_table[,c(2:11)] %>%
  pivot_longer(everything(), names_to = "Topic #", values_to = "Topic Proportions")

topics_label <- labelTopics(model.stm, n=10)
prob_word <- topics_label[["prob"]]

topic_long$`Top Words` <- ""
for (i in 1:10) {
  topic_long[i,3] <- paste(prob_word[i,], collapse = ", ")
}

topic_long$`Topic #` <- gsub("Topic", "", topic_long$`Topic #`)
topic_long$`Topic Proportions` <- round(topic_long$`Topic Proportions`*100)
topic_long$`Topic Proportions` <- paste0(topic_long$`Topic Proportions`, "%")

knitr::kable(topic_long)
```

## Exploring Content: Semi-Supervised Latent Dirichlet Allocation

```{r}
#| label: dictionary
#| warning: false
#| tbl-cap: Dictionary with different topics (seeds)

# Creating Dictionary
dict <- dictionary(list(middle_east = c("israel*", "palest*", "paläs*", 
                                        "jerusalem", "aqsa", "west bank", 
                                        "west-bank", "gaza", "aparth*", "antisemit*"),
                        other_grievances = c("china", "chines*", "uigur*", "uyghur*",
                                        "chines*", "camp*", "hindu*", "myanm*",
                                        "rohing*", "bosni*", "srebrenica", 
                                        "hindutv*", "bomb*", "attack", "strike"),
                        defence = c("verteid*", "resist*", "defen*", 
                                    "widerstand*", "battl*", "wehren*", 
                                    "abwehr*", "oppos*"),
                        hijab = c("kopftuch*", "scarf*", "niqab*", "jilbab*",
                                  "hijab*", "shador", "schador"),
                        racism_islamophobia = c("rassis*", "race*", "racis*", 
                                                "discrim*", "diskrim*", "nazi*", "*phob*"),
                        islam_general = c("dua", "quran", "koran", "hadith", "narration", "prophet*", "gesandter", 
                                   "rasul*", "sahaba*", "salaf", "kalif*", "mubarak", "eid", "deen")))

table_dict <- as.data.frame(matrix(ncol = 6, nrow = 14))
names(table_dict) <- c("middle_east", "other_grievances", "defence", "hijab", 
                       "racism_islamophobia", "islam_general")

table_dict$middle_east <- c(dict[["middle_east"]], rep("", 14-length(dict[["middle_east"]])))
table_dict$other_grievances <- c(dict[["other_grievances"]], rep("", 14-length(dict[["other_grievances"]])))
table_dict$defence <- c(dict[["defence"]], rep("", 14-length(dict[["defence"]])))
table_dict$hijab <- c(dict[["hijab"]], rep("", 14-length(dict[["hijab"]])))
table_dict$racism_islamophobia <- c(dict[["racism_islamophobia"]], rep("", 14-length(dict[["racism_islamophobia"]])))
table_dict$islam_general <- c(dict[["islam_general"]], rep("", 14-length(dict[["islam_general"]])))

# Print Dictionary
knitr::kable(table_dict)
```

```{r}
#| label: seeded-lda-1
#| warning: false
#| tbl-cap: 30 most used terms per topic (seed)

# Create Seeded LDA
tmod_slda <- textmodel_seededlda(dfm_post, dictionary = dict)

# Print Dictionary
knitr::kable(terms(tmod_slda, 30))
```

```{r}
#| label: seeded-lda-2
#| warning: false
#| tbl-cap: "Number of documents that most likely correspond respective topic (seed)"

dfm_seed <- dfm_post
dfm_seed$topic2 <- topics(tmod_slda)
knitr::kable(table(dfm_seed$topic2), col.names = c("Topic (Seed)", "Number of Tweets"))
```

## Classification: Keyness

```{r}
#| label: keyness
#| warning: false
#| fig-cap: "Analysis of relative frequency (keyness): Generation Islam (@genislam1) and Central Council of Muslims in Germany (@der_zmd)"


# Create Figure
key_df <- bind_rows(genislam, zmd)
key_df$screen_name <- factor(key_df$screen_name, levels = c("der_zmd", "genislam1"))

key_corp <- corpus(key_df)
key_dfm <- tokens(key_corp, remove_punct=T,
                  remove_numbers = T,
                  remove_url = T,
                  split_hyphens = T,
                  remove_symbols = T) %>%
  tokens_remove(stopwords("english", source = "marimo")) %>%
  tokens_remove(stopwords("de", source = "marimo")) %>%
  tokens_remove(stopwords("ar", source = "stopwords-iso")) %>%
  dfm() %>%
  dfm_group(groups = screen_name) %>%
  dfm_remove(pattern = c("*.tt", "*.uk", "*.com", "rt", "#*", "@*", ".de")) %>%
  dfm_trim(max_termfreq = .99,termfreq_type = "quantile",verbose = T) %>%
  dfm_trim(min_termfreq = .7,termfreq_type = "quantile",verbose = T)

result_keyness <- textstat_keyness(key_dfm, target = "genislam1")
textplot_keyness(result_keyness, color = c("black", "gray"))

# Saving Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "keyness.pdf"), 
          fallback_resolution=800, height =7, width = 9)
textplot_keyness(result_keyness, color = c("black", "gray"))
dev.off()
```

## Classification: Naïve Bayes

```{r}
#| label: confusion-matrix-1
#| warning: false
#| tbl-cap: "Confusion matrix for Naïve Bayes model"

key_df_small<- key_df
key_df_small<- key_df_small%>%
  select(text, screen_name)

data_corpus <- corpus(key_df_small, text_field = "text")
  
set.seed(1234)
training_id <- sample(1:4666, 2333, replace = FALSE)

# Create docvar with ID
docvars(data_corpus, "id_numeric") <- 1:ndoc(data_corpus)

# Get training set
dfmat_training <- corpus_subset(data_corpus, id_numeric %in% training_id) %>%
   tokens(remove_punct=T,
                  remove_numbers = T,
                  remove_url = T,
                  split_hyphens = T,
                  remove_symbols = T) %>%
  tokens_remove(stopwords("english", source = "marimo")) %>%
  tokens_remove(stopwords("de", source = "marimo")) %>%
  tokens_remove(stopwords("ar", source = "stopwords-iso")) %>%
  dfm() %>%
  dfm_remove(pattern = c("*.tt", "*.uk", "*.com", "rt", "#*", "@*", ".de")) %>%
  dfm_trim(max_termfreq = .99,termfreq_type = "quantile",verbose = T) %>%
  dfm_trim(min_termfreq = .7,termfreq_type = "quantile",verbose = T)

# Get test set (documents not in training_id)
dfmat_test <-
  corpus_subset(data_corpus,!id_numeric %in% training_id) %>%
   tokens(remove_punct=T,
                  remove_numbers = T,
                  remove_url = T,
                  split_hyphens = T,
                  remove_symbols = T) %>%
  tokens_remove(stopwords("english", source = "marimo")) %>%
  tokens_remove(stopwords("de", source = "marimo")) %>%
  tokens_remove(stopwords("ar", source = "stopwords-iso")) %>%
  dfm() %>%
  dfm_remove(pattern = c("*.tt", "*.uk", "*.com", "rt", "#*", "@*", ".de")) %>%
  dfm_trim(max_termfreq = .99,termfreq_type = "quantile",verbose = T) %>%
  dfm_trim(min_termfreq = .7,termfreq_type = "quantile",verbose = T)


# Train Naïve Bayes
model.NB <- textmodel_nb(dfmat_training, docvars(dfmat_training, "screen_name"), prior = "docfreq")

# The prior indicates an assumed distribution. 
# Here we choose how frequently the categories occur in our data.

dfmat_matched <-
  dfm_match(dfmat_test, features = featnames(dfmat_training))

actual_class <- docvars(dfmat_matched, "screen_name")
predicted_class <- predict(model.NB, newdata = dfmat_matched)
tab_class <- table(actual_class, predicted_class)

confusion <- confusionMatrix(tab_class, mode = "everything", positive = "genislam1")
confusion
```

```{r}
#| label: confusion-matrix-2
#| warning: false
#| fig-cap: "Displaying predicted and actual classes from Naïve Bayes model" 
confusion.data <- as.data.frame(confusion[["table"]])

# Creating Figure
level_order_y <-
  factor(confusion.data$actual_class,
         level = c("genislam1", "der_zmd"))

ggplot(confusion.data,
       aes(x = predicted_class, y = level_order_y, fill = Freq, label = Freq)) +
  xlab("Predicted") +
  ylab("Observed") +
  geom_tile() + theme_minimal() + coord_equal() +
  geom_label(fill = "white") +
  scale_fill_distiller(palette = "Greys", direction = 1, name = "Tweets")

# Saving Figure
ggsave("naive_bayes.pdf", path = file.path(getwd(), "figs"), device="pdf", dpi=800)
```

```{r}
#| label: confusion-matrix-3
#| warning: false
#| fig-cap: "Text elements with the most predicting power for Generation Islam" 

model_parm <- rownames_to_column(as.data.frame(model.NB[["param"]]), "screen_name")

model_parm_long <- model_parm %>%
  pivot_longer(-screen_name)

model_parm_long$value <- format(model_parm_long$value , scientific = FALSE)

top_ten_parameters <- model_parm_long %>%
  filter(screen_name == "genislam1") %>%
  slice_max(value, n=10)

top_ten_parameters$value <- as.numeric(top_ten_parameters$value)

ggplot(top_ten_parameters, aes(y = value, x = reorder(name,value))) +
  geom_col() +
  coord_flip() +
  xlab("Text elements") +
  ylab("Coefficient") +
  theme_minimal()

ggsave("nb_coef.pdf", path = file.path(getwd(), "figs"), device="pdf", dpi=800)
```

## Classification: Glmnet and Random Forest

### Descriptive Data

```{r}
#| label: grievance-prediction-1
#| warning: false
#| tbl-cap: "Number of Tweets corresponding with grievances"
#| 

# Create Wordlist inspired by Seeded-LDA
grievance <- c("israel", "palest", "paläs", "jerusalem", "aqsa", "west bank",
               "west-bank", "gaza", "aparth", "antisemit","uigur", "uyghur",
               "hindut", "myanm", "rohing", "srebrenica", "bomb", "attack", 
               "strike", "verteid", "resist", "defen", "widerstand", "battl",
               "wehren", "abwehr", "oppos", "kopftuch", "scarf", "niqab",
               "jilbab","hijab", "shador", "schador", "rassis", "race", "racis",
               "discrim", "diskrim", "nazi", "phob")

all_islam$grievance <- grepl(paste(grievance,collapse="|"), all_islam$text, ignore.case = TRUE)

all_islam <- all_islam %>%
  mutate(account = case_when(screen_name == "genislam1" ~ "genislam",
                             TRUE ~ "other"))
# Creating Table
knitr::kable(all_islam %>%
    group_by(account, grievance) %>%
    summarise(n = n()) %>%
    mutate(freq = paste0(round(n / sum(n)*100), "%")), caption = "Relative and absolute frequency of tweets corresponding with grievances")
```

### Lasso and Elastic-Net Regularized Generalized Linear Models (glmnet)

```{r}
#| label: grievance-prediction-2
#| warning: false

## Fitting a glmnet model with more variables
set.seed(1234)
account_y <- factor(all_islam$account, levels = c("other", "genislam"))
account_x <- select(all_islam, grievance,display_text_width, 
                    retweet_count, favorite_count)

# Create custom indices: myFolds (for a 10-fold CV)
myFolds <- createFolds(account_y, k = 10)

# Create reusable trainControl object: myControl
myControl <- trainControl(
  summaryFunction = twoClassSummary,
  classProbs = TRUE, # IMPORTANT!
  verboseIter = TRUE,
  savePredictions = TRUE,
  index = myFolds
)

train <- data.frame(account_x, account_y) 

#glmnet
model_glmnet <- train(account_y ~ ., data = train,
  metric = "ROC",
  method = "glmnet",
  trControl = myControl,
  tuneGrid = expand.grid(
    alpha=seq(0,1,0.25), # 5 values of alpha
    lambda=seq(0.0001, 1, length=20) # 20 values of lambda
  )
)

# Displaying the highest ROC
max(model_glmnet$results[["ROC"]])

# Displaying coefficients
coef(model_glmnet$finalModel, s = -1.008148)
```

### Model Comparison: Glmnet and Random Forest

```{r}
#| label: grievance-prediction-3
#| warning: false
#| fig-cap: "Model comparison of Glmnet and Random Forest"

## Optimizing predictions with random forest
set.seed(1234)
#random forest
model_rf <- train(account_y ~ ., data = train,
  metric = "ROC",
  method = "ranger",
  trControl = myControl
)

# Create model_list
model_list <- list(glmnet = model_glmnet, rf = model_rf)

# Pass model_list to resamples()
resamples <- resamples(model_list)

# Summarize the results
summary(resamples)

# RF performs best, also outlier folds (see spikes and near zero values)
bwtheme <- standard.theme("pdf", color=FALSE)
bwtheme <- bwtheme
bwtheme$par.main.text <- list(font = 2,
                       just = "left", 
                       x = grid::unit(5, "mm"))
glm_plot1 <- bwplot(resamples, metric="ROC", par.settings=bwtheme, main="A")
glm_plot1[["xlab"]] <- "AUC"
glm_plot2 <- dotplot(resamples, metric = "ROC", par.settings=bwtheme, main="B")
glm_plot2[["xlab"]] <- "AUC"
glm_plot3 <- xyplot(resamples, metric="ROC", par.settings=bwtheme)
glm_plot3[["xlab"]] <- "AUC"
glm_plot3[["main"]] <- "C"
glm_plot4 <- densityplot(resamples, metric="ROC", ylab="Density", par.settings=bwtheme, main="D")
glm_plot4[["xlab"]] <- "AUC"

# Creating Figure
grid.arrange(glm_plot1,glm_plot2, glm_plot3, glm_plot4, ncol=2, bottom ="All values display AUC (ROC)")

# Saving Figure
cairo_pdf(paste0(file.path(getwd(), "figs"), "/", "model_stack.pdf"), 
          fallback_resolution=800, height =7, width = 9)
grid.arrange(glm_plot1,glm_plot2, glm_plot3, glm_plot4, ncol=2, bottom ="All values display ROC")
dev.off()
```

### Stacking Glmnet and Random Forest to improve predictions

```{r}
#| label: grievance-prediction-4
#| warning: false
#| fig-cap: "Displaying predicted and actual classes from stacking Glment and Random Forest"
#| 
set.seed(1234)
training_id_new <- sample(1:11425, 5712, replace = FALSE)
train_new <- train[training_id_new,]
test_new <- train[-training_id_new,]

myFolds <- createFolds(train_new$account_y, k = 10)

myControl <- trainControl(
  summaryFunction = twoClassSummary,
  classProbs = TRUE, # IMPORTANT!
  verboseIter = TRUE,
  savePredictions = TRUE,
  index = myFolds
)


models <- caretList(account_y ~ ., data=train_new, trControl = myControl, methodList=c("glmnet", "ranger"))

# Create ensemble model: stack
stack <- caretStack(models, method="glm")

# Look at summary
summary(stack)

test_new$pred <- predict(stack, newdata=test_new, level = 0.95)
confusionMatrix(data = test_new$pred, reference = test_new$account_y, positive = "genislam")
confusion_new <- confusionMatrix(data = test_new$pred, reference = test_new$account_y, positive = "genislam")

confusion.data.new <- as.data.frame(confusion_new[["table"]])

# Creating Figure
level_order_y <-
  factor(confusion.data.new$Reference,
         level = c("genislam", "other"))

ggplot(confusion.data.new,
       aes(x = Prediction, y = level_order_y, fill = Freq, label = Freq)) +
  xlab("Predicted") +
  ylab("Observed") +
  geom_tile() + theme_minimal() + coord_equal() +
  geom_label(fill = "white") +
  scale_fill_distiller(palette = "Greys", direction = 1, name = "Tweets")

# Saving Figure
ggsave("caret_stack.pdf", path = file.path(getwd(), "figs"), device="pdf", dpi=800)
```
